Understanding the nanoscale structure of hexagonal phase lyotropic liquid crystal membranes

### 2017-09-13 Ben_Manuscripts/Paper1/Outline.tex
Outline updates

\documentclass{article}
\usepackage{graphicx}
\usepackage{wrapfig}
\usepackage{subcaption}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath} % or simply amstext
\usepackage{siunitx}
\usepackage{booktabs}
\usepackage[export]{adjustbox}
\newcommand{\angstrom}{\textup{\AA}}
\usepackage{cleveref}
\usepackage{booktabs}
\usepackage{gensymb}
\usepackage{float}
%MRS: paper needs a conclusions section outlined.
%MRS: maybe replace pi with $\pi$,qz with $q_z$, and \angstrom by \angstrom~ (the tilde is an enforced space)
%MRS: also maybe \AA instead of \angstrom?  I can't remember which formats better in text.
%\title{Predicting Transport in Lyotropic Liquid Crystal Membranes with Molecular Dynamics Simulations -- Outline}
%MRS: focus isn't really on transport, but on what the strucures are.
\title{Understanding the nanoscale structure of hexagonal phase lyotropic liquid crystal membranes}
%MRS: I don't know that we need to put MD simulations alone in the title, since we also do a fair amount of comparison to experiment. 
\author{Benjamin J. Coscia \and Douglas L. Gin \and Richard D. Noble \and Joe Yelk \and Matthew Glaser \and Xunda Feng \and Michael R. Shirts} 
\begin{document}
  \bibliographystyle{ieeetr}
  \graphicspath{{./figures/}}
  \maketitle
  \section*{Introduction}

@@

  (2) If layers do exist, how many monomers constitute a single layer?
  There has been definitive answer to the question in literature.
%   We do not know the number of monomers that constitute the layers which stack
%   on top of each other to create pores.
  \begin{itemize}
%     \item The Col\textsubscript{h} phase is described as having pores made of
%     disks or layers stacked on top of one another, each containing a set 
%     number of monomers. 
    \item A simple simulation study of a similar molecule 
%MRS: suggests isn't the right word, since that implies it may still be valid, which probably isn't correct.  I would probably say how simple that test was, since what they did had almost no chance of getting the right answer in the proper context. We thought they did something reasonable, but they really didn't. 
%suggests
%BJC: Okay, added a little more to emphasize that what they did isn't really useful.
suggested
    that there are 4 monomers in each layer. Their estimation is based on a
    simulated system containing only 16 total monomers which likely does not sufficiently
    model the chemical environment present in the real system.~\cite{zhu_methacrylated_2006}. 
    \item A separate calculation based on the volume of the liquid crystal monomers proposes
    that there are seven monomers in each layer~\cite{resel_structural_2000}. 
    \item A molecular model has the best chance of directly answering this question.
  \end{itemize}
%MRS: phrasing
    %\item Once we know the number of monomers in each layer, we still do not know how

    (3) How do monomers in each layer position themselves with respect to surrounding 
    layers?
%     Even if we knew the number of monomers in each layer, we still would not know how 
%     monomers in each layer are positioned with respect to other layers. 
    \begin{itemize}
      \item A driving force of self assembly in this system is thought to be pi-pi
      stacking interactions between aromatic headgroups \cite{gazit_possible_2002}. 
      \item Gas phase ab initio studies of benzene dimers have shown a clear energetic
      advantage for parallel displaced and T-shaped pi-pi stacking conformations versus a
      sandwiched conformation ~\cite{sinnokrot_estimates_2002}.
      \item Substituted benzene rings exhibit an even stronger pi-pi stacking 
      attraction which favors the parallel displaced configuration in all cases
      except where the substitutions are extremely electron withdrawing
      \cite{waller_hybrid_2006,ringer_effect_2006}.
    \end{itemize}

@@

  The timescale for self assembly of monomers into the hexagonal phase is
  unknown and likely outside of a reasonable length for an atomistic
  simulation, calling for a more efficient way to build the system. 
  \begin{itemize}
    \item Previous work has shown a coarse grain model self assemble into
    the H\textsubscript{II} phase configuration in $\approx$ 1000 ns \cite{mondal_self-assembly_2013}.
    \item We attempted atomistic self-assembly by packing monomers into a box 
    using Packmol \cite{martinez_packmol:_2009}.
    \item Simulations of greater than 100 ns show no indicators of progress 
    towards an ordered system.
    \item To bypass the slow self-assembly process, python scripts are used
    to assemble monomers into a structure close 
    %MRS:
    %to the expected equilibrium configuration. 
    to one of a number of hypothesized equilibrium configurations (Figure~\ref{fig:python}).
    \item A short, restrained equilibration, followed by NPT simulations 
    between 400 and 500 ns, allows the initial configuration to relax into
    an equilibrium configuration.
    \item Our logic for choosing a starting configuration and the details 
    of the equilibration schemes are presented below.
  \end{itemize}

@@

  %MRS: initial layer spacing.
  We chose a layer spacing based on experimental 2D WAXS data.
  \begin{itemize}  
    \item The pattern shows reflections corresponding to features spaced 3.7 \angstrom~apart.
    \item It has been hypothesized that the features are a result of pi-pi
    interactions between stacked aromatic rings \cite{feng_scalable_2014}. 
    \item Our simulations tend to equilibrate to a wider interlayer spacing of
    $\approx$ 4.1 \angstrom, which inspired separate systems starting with layer 
    spacings greater than 4 \angstrom.
  \end{itemize}

@@

  An equilibration scheme with position restraints placed on aromatic rings
  %MRS: 
  %prevents 
  during early equilibration steps is required to prevent high energy repulsions .
  %MRS: should be clearer what you mean by ``unrealistic jumps''.  Hard to visualize.
  %BJC: 'high energy repulsions' ?
  \begin{itemize}
    \item Restraints fix monomer head groups in the sandwiched or parallel-displaced
    configurations while allowing monomer tails to settle.
    \item Doing so also mitigates system dependence on initial monomer configuration.
    \item The restrained portion of the equilibration scheme is run in the NVT ensemble.
    \item Every 50 ps, we reduce the force constants by the square root of its 
    previous value, starting from 1e6 KJ mol\textsuperscript{-1} nm\textsuperscript{-2}.
    \item Once the force constant is below 10 KJ mol\textsuperscript{-1} 
    nm\textsuperscript{-2}, the restraints are slowly released until there is no more 
    restraining potential.  
    \item The resulting unrestrained structure is allowed to equilibrate further in the NPT
    ensemble for 400 - 500 ns.
   %BJC: I will reference an equilibration script that can be released with the supplemental info
   %MRS: we should release as many scripts as is feasible, can be in a github repository.
   %BJC: Okay, once we submit, I will need to spend some time cleaning the scripts
   %MRS: You've described two equilibration procedures (or two varieties of the same one?) - need to be crystal clear to the reader as to which is used where.
   %BJC: Yea I'm just saying that I do 50 ps restrained simulations in NVT ensemble and then once the restraints are gone I switch to NPT. I edited the language to try and make it clearer.
  \end{itemize}

  %BJC: the following paragraph will be replaced with something that Joe writes
  %MRS: sounds good.
  Simulated X-ray diffraction patterns were generated based on atomic
  coordinates for a direct experimental comparison.
  \begin{itemize}
    \item All atomic coordinates were simulated as gaussian spheres of electron
    density corresponding to each atom's atomic number.
    \item A three dimensional fourier transform (FT) of the array of electron 
    density results in a three dimensional structure factor which represents
    the unit cell in reciprocal space.
    \item We perform an angular average of the structure factor about the 
    z axis to generate a 2D cross section close to what one would see 
    experimentally.
    \item We matched experimental 2D WAXS patterns by iterative improvement
    of our choice of initial structure and equilibration procedure.
  \end{itemize}

  \begin{figure}[!ht]
	\centering
	\begin{subfigure}[b]{0.32\textwidth}
		\centering
		\includegraphics[width=\textwidth]{sandwiched.png}
		\caption{}\label{fig:sandwiched}
	\end{subfigure}
	\begin{subfigure}[b]{0.32\textwidth}
		\centering
		\includegraphics[width=\textwidth]{PD.png}
		\caption{}\label{fig:pd}
	\end{subfigure}
	\begin{subfigure}[b]{0.32\textwidth}
		\centering
		\includegraphics[width=\textwidth]{Tshaped.png}
		\caption{}\label{fig:tshaped}
	\end{subfigure}
	\vskip\baselineskip
	\begin{subfigure}[b]{0.475\textwidth}
		\centering
		\includegraphics[width=\textwidth]{sandwichedlayers.png}
		\caption{}\label{fig:sandwichedlayers}
	\end{subfigure}
	\begin{subfigure}[b]{0.475\textwidth}
		\centering
		\includegraphics[width=\textwidth]{offsetlayers.png}
		\caption{}\label{fig:offsetlayers}
	\end{subfigure}
	\caption{(a) Sandwiched benzene dimers stack 3.8 \angstrom apart. (b) Parallel-Displaced benzene dimers stack
	3.4 \angstrom vertically and 1.6 \angstrom horizontally apart. (c) T-shaped benzene dimers stack 5.0 \angstrom apart. 
	(d) Two monomer layers stacked in the sandwiched configuration (e) Two monomer layers stacked in the parallel-displaced
	configuration }\label{fig:stacking}
  \end{figure}

@@

  Using an equilibrated structure, a crosslinking procedure was performed
  in order to better parallel synthetic procedures. 
  \begin{itemize}
    \item The purpose of crosslinking is to maintain macroscopic alignment of 
    the crystalline domains, ensuring aligned, hexagonally packed pores.
    \item For that reason, we are not concerned with replicating the kinetics 
    of the reaction, but instead emphasize the consistency of the final structure
    with experimental structural data.
    \item The algorithm was developed based on the known reaction mechanism.
    \item Crosslinking of this system is a free radical polymerization (FRP)
    taking place between terminal vinyl groups present on each of the three
    monomer tails.
    \item FRPs require an initiator which bonds to the system, meaning new atoms
    were introduced into the system.
    \item For simplicity, the initiator was simulated as hydrogen and made present 
    in the simulation by including them in all possible bonding positions as dummy atoms.
    \item The crosslinking procedure is carried out iteratively.
    \item During each iteration, bonding carbon atoms are chosen based on a distance cut-off.
    \item The topology is updated with new bonds and dummy hydrogen atoms are 
    changed to appropriate hydrogen types. 
    \item Head-to-tail addition was the only propagation mode considered due to 
    its dominance the real system.
    \item Direction of attack was not considered because the resultant mixture 
    is racemic.
    %BJC: The following items belongs in results/discussion
    %MRS: probably. 
    \item The resulting crosslinked structure has an even distribution of
    crosslinks between monomer tails of the same monomer, monomers stacked on
    top of each other and monomers in other pores, including across periodic
    boundaries.
    \item The pore spacing shrinks by $\approx$ 1 \angstrom and stays 
    constant under a range of simulation conditions.
  \end{itemize}

@@

  \begin{table}[h]
  \centering
  \begin{tabular}{ccc}
  \toprule
  		   & \multicolumn{2}{c}{Starting Configuration} \\
  \hline
  Monomers per layer & Sandwiched & Parallel Displaced \\
  \midrule
  4 & $3.71 \pm 0.04$ & $3.82 \pm 0.03$ \\
  5 & $4.20 \pm 0.04$ & $4.23 \pm 0.04$ \\
  6 & $4.83 \pm 0.03$ & $4.85 \pm 0.02$ \\
  7 & $4.73 \pm 0.03$ & $4.84 \pm 0.03$ \\
  8 & $5.08 \pm 0.04$ & $5.46 \pm 0.03$ \\
  \bottomrule
  \end{tabular}
  \caption{The pore spacing 
  %MRS added
  (given in \angstrom)
  of the model increases as number of monomers
  in each layer increases. The pore spacing of a system starting in the 
  sandwiched configuration is systematically lower than that started in an 
  offset configuration. Systems built with 5 monomers per layer in a parallel
  displaced configuration result in a pore spacing closest 
  %MRS: clarified.
  %to experimental data
  to the experimental 4.12 \angstrom}\label{table:p2p} 
  \end{table}

@@

  Experimental WAXS measurements encode all structural details. 
  %MRS: also encodes the pore spacing
  %BJC: got rid of 'remaining' in 'remaining structural details'
  %BJC: I'm not exactly sure where to place this paragraph. Maybe it can go in methods?
  \begin{itemize}
  	\item There are five major features present in the 2D experimental 
	pattern which our model intends to reproduce (Figure~\ref{fig:WAXS}).
	\item The first is located at qz = 1.7 \angstrom \textsuperscript{-1},
	corresponding to a real spacing of 3.7 \angstrom. The reflection is 
	attributed to pi-pi stacking between aromatic rings in the direction
	perpendicular to the membrane plane, or z-axis. For simplicity, this 
	reflection will be referred to as R-$\pi$.
        %MRS: why R in R-pi? for reflection?
	%BJC: yes, R = reflection
	\item A weak intensity line is located at exactly half the qz value of
	R-$\pi$ (qz = 0.85 \angstrom$^-1$), corresponding to a 
        %MRS: or could use \angstrom$^-1$ instead of \textsuperscript{-1} 
	real space periodic spacing of 7.4 \angstrom. This reflection has been 
	interpreted  as 2\textsubscript{1} helical ordering of aromatic rings 
	along the z axis meaning if the positions of the aromatic rings can
	be traced by a helix, then for each turn in the helix, there should be
	two aromatic rings. For this reason it will be referred to as R-helix.
	\item A third major reflection is marked by a low intensity ring located
	at r = 1.4 \angstrom \textsuperscript{-1}. The real space separation 
	corresponds to 4.5 \angstrom which is characteristic of the average 
	spacing between packed alkane chains. This reflection will be called R-alkanes.
	\item Within R-alkanes, are four spots of higher intensity which 
	will be called R-spots. All are located $\approx 40$ degrees from the qz axis
	in their respective quadrants. In many liquid crystal systems this can be
	explained by the tilt angle of the alkane chains with respect to the xy plane. % BJC: Reference
	\item The final major reflections correspond to the spacing and symmetry of 
	the d\textsubscript{100} plane which can be related to the distance between
	pores. The feature, which will be called R-pores, is characterized by dots 
	along qz = 0. The spacing between dots is indicative of the hexagonal 
	symmetry of the packed pores. It is easiest to interpret the data by 
	radially integrating the 2D data to get a 1D curve which is shown in Figure~\ref{fig:SAXS}.
  \end{itemize}

@@

  The initial distance between layers can influence the approach towards
  equilibrium. 
  \begin{itemize}
  	\item Our choice of distance between layers results in long-term stability of 
	different configurations indicating that we have found more than one metastable
	free energy basin.
  	\item Equilibrated systems built according to the 3.7 \angstrom 
	layer spacing implied by R-$\pi$ are characterized by a defined, cylindrical and
	open pore structure.
	\item Aromatic rings are arranged in a helical conformation.%BJC: could potentially support with a figure. Mentioning the helical arrangmentment might makes things confusing though
        %MRS: 'basin' is not that common a term, and also only makes sense if one explicitly states what 
        %MRS: the basin is with respect to. 
	%BJC: added sentence to beginning of paragraph
        \item We will refer to this large set of configurations, with an open helical pore, as Basin A (Figure~\ref{fig:abasin}).
        %\item We will refer to this system as
        %MRS: maybe Basin O and Basin C for open and closed?
	%BJC: That works but 'capital oh' might get confused with zero
	\item Simulations of systems built with layers stacked greater than 4 
	\angstrom apart results in a pore structure characterized by high radial 
	disorder, while still maintaining partitioning between hydrophobic and 
	hydrophilic regions.
        %MRS: see above for clarifying ``basins''.
	\item This will be called Basin B (Figure~\ref{fig:bbasin}).
        %MRS: I don't think enough information has been presented to the reader yet for this to be 'apparent'.
	\item This LLC membrane may exist in at least two metastable states.
	\item The distinct difference in pore structure exhibited by each phase will 
	likely lead to different transport mechanisms.
	\item Because the pore structure will vary between each Basin, understanding 
	which phase exists experimentally is necessary in order to ensure we are 
	studying the system which actually dominates.  %MRS: remind people why.
  \end{itemize}

>>>>

\documentclass{article}
\usepackage{graphicx}
\usepackage{wrapfig}
\usepackage{subcaption}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath} % or simply amstext
\usepackage{siunitx}
\usepackage{booktabs}
\usepackage[export]{adjustbox}
\newcommand{\angstrom}{\textup{\AA}}
\usepackage{cleveref}
\usepackage{booktabs}
\usepackage{gensymb}
\usepackage{float}
\title{Understanding the nanoscale structure of hexagonal phase lyotropic liquid crystal membranes}
\author{Benjamin J. Coscia \and Douglas L. Gin \and Richard D. Noble \and Joe Yelk \and Matthew Glaser \and Xunda Feng \and Michael R. Shirts} 
\begin{document}
  \bibliographystyle{ieeetr}
  \graphicspath{{./figures/}}
  \maketitle
  \section*{Introduction}

@@

  (2) If layers do exist, how many monomers constitute a single layer?
  There has been no definitive answer to the question in literature.
%   We do not know the number of monomers that constitute the layers which stack
%   on top of each other to create pores.
  \begin{itemize}
%     \item The Col\textsubscript{h} phase is described as having pores made of
%     disks or layers stacked on top of one another, each containing a set 
%     number of monomers. 
    \item A simple simulation study of a similar molecule 
%MRS: suggests isn't the right word, since that implies it may still be valid, which probably isn't correct.  I would probably say how simple that test was, since what they did had almost no chance of getting the right answer in the proper context. We thought they did something reasonable, but they really didn't. 
%suggests
%BJC: Okay, added a little more to emphasize that what they did isn't really useful.
suggested
    that there are 4 monomers in each layer. Their estimation is based on a
    simulated system containing only 16 total monomers which likely does not sufficiently
    model the chemical environment present in the real system.~\cite{zhu_methacrylated_2006}. 
    \item A separate calculation based on the volume of the liquid crystal monomers proposes
    that there are seven monomers in each layer~\cite{resel_structural_2000}. 
    \item A molecular model has the best chance of directly answering this question.
  \end{itemize}
%MRS: phrasing
    %\item Once we know the number of monomers in each layer, we still do not know how

    (3) How do monomers in each layer position themselves with respect to surrounding 
    layers?
%     Even if we knew the number of monomers in each layer, we still would not know how 
%     monomers in each layer are positioned with respect to other layers. 
    \begin{itemize}
      \item A driving force of self assembly in this system is thought to be $\pi$-$\pi$
      stacking interactions between aromatic headgroups \cite{gazit_possible_2002}. 
      \item Gas phase ab initio studies of benzene dimers have shown a clear energetic
      advantage for parallel displaced and T-shaped $\pi$-$\pi$ stacking conformations versus a
      sandwiched conformation ~\cite{sinnokrot_estimates_2002}.
      \item Substituted benzene rings exhibit an even stronger $\pi$-$\pi$ stacking 
      attraction which favors the parallel displaced configuration in all cases
      except where the substitutions are extremely electron withdrawing
      \cite{waller_hybrid_2006,ringer_effect_2006}.
    \end{itemize}

@@

  The timescale for self assembly of monomers into the hexagonal phase is
  unknown and likely outside of a reasonable length for an atomistic
  simulation, calling for a more efficient way to build the system. 
  \begin{itemize}
    \item Previous work has shown a coarse grain model self assemble into
    the H\textsubscript{II} phase configuration in $\approx$ 1000 ns \cite{mondal_self-assembly_2013}.
    \item We attempted atomistic self-assembly by packing monomers into a box 
    using Packmol \cite{martinez_packmol:_2009}.
    \item Simulations of greater than 100 ns show no indicators of progress 
    towards an ordered system.
    \item To bypass the slow self-assembly process, python scripts are used
    to assemble monomers into a structure close 
    %MRS:
    %to the expected equilibrium configuration. 
    to one of a number of hypothesized equilibrium configurations (Figure~\ref{fig:python}).
    %\item A short, restrained equilibration, followed by NPT simulations 
    %between 400 and 500 ns, allows the initial configuration to relax into
    %an equilibrium configuration.
    %\item Our logic for choosing a starting configuration and the details
    %of the equilibration schemes are presented below.
   \end{itemize}

  We tested a number of equilibration schemes in an effort to match experiment
  while overcoming kinetic limitations of such a large system that can easily
  get stuck in multiple metastable states.
    Equilibration Scheme A:
    \item Apply position restraints to aromatic rings in order to maintain
    orientational order. 
    \item A short, restrained equilibration, followed by NPT simulations 
    between 400 and 500 ns, allows the initial configuration to relax into
    an equilibrium configuration.
    \item Our logic for choosing a starting configuration and the details 
    of the equilibration schemes are presented below.
  \end{itemize}

@@

  %MRS: initial layer spacing.
  We chose a layer spacing based on experimental 2D WAXS data.
  \begin{itemize}  
    \item The pattern shows reflections corresponding to features spaced 3.7 \angstrom~apart.
    \item It has been hypothesized that the features are a result of $\pi$-$\pi$
    interactions between stacked aromatic rings \cite{feng_scalable_2014}. 
    \item Our simulations tend to equilibrate to a wider interlayer spacing of
    $\approx$ 4.1 \angstrom~, which inspired separate systems starting with layer 
    spacings greater than 4 \angstrom~.
  \end{itemize}

@@

  We tested a number of equilibration schemes of increasing complexity in an effort
  to match experiment while overcoming kinetic limitations of such a large system 
  that can easily get stuck in multiple metastable states. All start from an initial
  configuration generated with chosen structure variables. 
  \begin{itemize}
      \item Equilibration Scheme A:
      \begin{itemize}
          \item Steepest descent energy minimization
          \item Short NPT simulation (~ 5 ns ) with berendsen barostat (tau-p = 1) at 300 K 
          \item Switch to Parrinello-Rahman (tau-p = 10) and run NPT simulation for 400 - 500 ns
          %\item Final structure strongly influenced by monomer configuration used to build 
      \end{itemize}
      \item Equilibration Scheme B:
      \begin{itemize}
          \item Restraints fix monomer head groups in the sandwiched or parallel-displaced
          configurations while allowing monomer tails to settle.
          \item Doing so also mitigates system dependence on initial monomer configuration.
          \item The restrained portion of the equilibration scheme is run in the NVT ensemble.
          \item Every 50 ps, we reduce the force constants by the square root of its
          previous value, starting from 1e6 KJ mol$^-1$ nm$^-2$.
          \item Once the force constant is below 10 KJ mol$^-1$ nm$^-2$, the restraints are
          slowly released until there is no more restraining potential.
          \item The resulting unrestrained structure is allowed to equilibrate further in the NPT
          ensemble for 400 - 500 ns in the same way as Scheme A.
      \end{itemize}
      \item Equilibration Scheme C:
      \begin{itemize} 
          \item A system equilibrated according to scheme B is cut in half so we can access
          longer simulation timescales
          \item The system is simulated at 335K, close to its isotropic transition temperature, for 200 ns. % BJC: not entirely sure if it needs to be an already equilibrate structure
          \item The structure is then linearly cooled back down to 300 K over 500 ns. 
          \item The system size is doubled back to its original size and equilibrated for 200 ns at 300 K.
          \item Tried with and without an applied electric field.
      \end{itemize}
      \item Equilibration Scheme D:
      \begin{itemize}
          \item Even in the near dry Col\textsubscript{h} system, there exists an
          equilibrium concentration of water.
          \item The hydrogen bonding network formed by the water may play a role 
          in structuring the pore.
          \item We obtained an estimate of equilibrium pore water content by solvating
          an initial configuration with water baths above and below the membrane. 
	  \item We ran the solvated system according to Scheme A but for 1000 ns
          \item Using that number we added water to the pores of an initial 
	  configuration and equilibrated according to scheme B. 
      \end{itemize}
      \item In all cases, the v-rescale thermostat was used with tau-t = 0.1
  \end{itemize}

%  An equilibration scheme with position restraints placed on aromatic rings
  %MRS: 
  %prevents 
%  during early equilibration steps is required to prevent high energy repulsions .
  %MRS: should be clearer what you mean by ``unrealistic jumps''.  Hard to visualize.
  %BJC: 'high energy repulsions' ?
%  \begin{itemize}
%    \item Restraints fix monomer head groups in the sandwiched or parallel-displaced
%    configurations while allowing monomer tails to settle.
%    \item Doing so also mitigates system dependence on initial monomer configuration.
%    \item The restrained portion of the equilibration scheme is run in the NVT ensemble.
%    \item Every 50 ps, we reduce the force constants by the square root of its 
%    previous value, starting from 1e6 KJ mol\textsuperscript{-1} nm\textsuperscript{-2}.
%    \item Once the force constant is below 10 KJ mol\textsuperscript{-1} 
%    nm\textsuperscript{-2}, the restraints are slowly released until there is no more 
%    restraining potential.  
%    \item The resulting unrestrained structure is allowed to equilibrate further in the NPT
%    ensemble for 400 - 500 ns.
   %BJC: I will reference an equilibration script that can be released with the supplemental info
   %MRS: we should release as many scripts as is feasible, can be in a github repository.
   %BJC: Okay, once we submit, I will need to spend some time cleaning the scripts
   %MRS: You've described two equilibration procedures (or two varieties of the same one?) - need to be crystal clear to the reader as to which is used where.
   %BJC: Yea I'm just saying that I do 50 ps restrained simulations in NVT ensemble and then once the restraints are gone I switch to NPT. I edited the language to try and make it clearer.
%  \end{itemize}

  %BJC: the following paragraph will be replaced with something that Joe writes
  %MRS: sounds good.
  Simulated X-ray diffraction patterns were generated based on atomic
  coordinates for a direct experimental comparison.
  \begin{itemize}
    \item All atomic coordinates were simulated as gaussian spheres of electron
    density corresponding to each atom's atomic number.
    \item A three dimensional fourier transform (FT) of the array of electron 
    density results in a three dimensional structure factor which represents
    the unit cell in reciprocal space.
   % \item We perform an angular average of the structure factor about the 
    z axis to generate a 2D cross section close to what one would see 
    experimentally.
    \item We matched experimental 2D WAXS patterns by iterative improvement
    of our choice of initial structure and equilibration procedure.
  \end{itemize}

  \begin{figure}[!ht]
	\centering
	\begin{subfigure}[b]{0.32\textwidth}
		\centering
		\includegraphics[width=\textwidth]{sandwiched.png}
		\caption{}\label{fig:sandwiched}
	\end{subfigure}
	\begin{subfigure}[b]{0.32\textwidth}
		\centering
		\includegraphics[width=\textwidth]{PD.png}
		\caption{}\label{fig:pd}
	\end{subfigure}
	\begin{subfigure}[b]{0.32\textwidth}
		\centering
		\includegraphics[width=\textwidth]{Tshaped.png}
		\caption{}\label{fig:tshaped}
	\end{subfigure}
	\vskip\baselineskip
	\begin{subfigure}[b]{0.475\textwidth}
		\centering
		\includegraphics[width=\textwidth]{sandwichedlayers.png}
		\caption{}\label{fig:sandwichedlayers}
	\end{subfigure}
	\begin{subfigure}[b]{0.475\textwidth}
		\centering
		\includegraphics[width=\textwidth]{offsetlayers.png}
		\caption{}\label{fig:offsetlayers}
	\end{subfigure}
	\caption{(a) Sandwiched benzene dimers stack 3.8 \angstrom~apart. (b) Parallel-Displaced benzene dimers stack
	3.4 \angstrom~vertically and 1.6 \angstrom~horizontally apart. (c) T-shaped benzene dimers stack 5.0 \angstrom~apart. 
	(d) Two monomer layers stacked in the sandwiched configuration (e) Two monomer layers stacked in the parallel-displaced
	configuration }\label{fig:stacking}
  \end{figure}

@@

  Using an equilibrated structure, a crosslinking procedure was performed
  in order to better parallel synthetic procedures. 
  \begin{itemize}
    \item The purpose of crosslinking is to maintain macroscopic alignment of 
    the crystalline domains, ensuring aligned, hexagonally packed pores.
    \item For that reason, we are not concerned with replicating the kinetics 
    of the reaction, but instead emphasize the consistency of the final structure
    with experimental structural data.
    \item The algorithm was developed based on the known reaction mechanism.
    \item Crosslinking of this system is a free radical polymerization (FRP)
    taking place between terminal vinyl groups present on each of the three
    monomer tails.
    \item FRPs require an initiator which bonds to the system, meaning new atoms
    were introduced into the system.
    \item For simplicity, the initiator was simulated as hydrogen and made present 
    in the simulation by including them in all possible bonding positions as dummy atoms.
    \item The crosslinking procedure is carried out iteratively.
    \item During each iteration, bonding carbon atoms are chosen based on a distance cut-off.
    \item The topology is updated with new bonds and dummy hydrogen atoms are 
    changed to appropriate hydrogen types. 
    \item Head-to-tail addition was the only propagation mode considered due to 
    its dominance the real system.
    \item Direction of attack was not considered because the resultant mixture 
    is racemic.
    %BJC: The following items belongs in results/discussion
    %MRS: probably. 
    \item The resulting crosslinked structure has an even distribution of
    crosslinks between monomer tails of the same monomer, monomers stacked on
    top of each other and monomers in other pores, including across periodic
    boundaries.
    \item The pore spacing shrinks by $\approx$ 1 \angstrom~ and stays 
    constant under a range of simulation conditions.
  \end{itemize}

@@

  \begin{table}[h]
  \centering
  \begin{tabular}{ccc}
  \toprule
  		   & \multicolumn{2}{c}{Starting Configuration} \\
  \hline
  Monomers per layer & Sandwiched & Parallel Displaced \\
  \midrule
  4 & $3.71 \pm 0.04$ & $3.82 \pm 0.03$ \\
  5 & $4.20 \pm 0.04$ & $4.23 \pm 0.04$ \\
  6 & $4.83 \pm 0.03$ & $4.85 \pm 0.02$ \\
  7 & $4.73 \pm 0.03$ & $4.84 \pm 0.03$ \\
  8 & $5.08 \pm 0.04$ & $5.46 \pm 0.03$ \\
  \bottomrule
  \end{tabular}
  \caption{The pore spacing 
  %MRS added
  (given in \angstrom~)
  of the model increases as number of monomers
  in each layer increases. The pore spacing of a system starting in the 
  sandwiched configuration is systematically lower than that started in an 
  offset configuration. Systems built with 5 monomers per layer in a parallel
  displaced configuration result in a pore spacing closest 
  %MRS: clarified.
  %to experimental data
  to the experimental 4.12 \angstrom~}\label{table:p2p} 
  \end{table}

@@

  Experimental WAXS measurements encode all structural details. 
  %MRS: also encodes the pore spacing
  %BJC: got rid of 'remaining' in 'remaining structural details'
  %BJC: I'm not exactly sure where to place this paragraph. Maybe it can go in methods?
  \begin{itemize}
  	\item There are five major features present in the 2D experimental 
	pattern which our model intends to reproduce (Figure~\ref{fig:WAXS}).
	\item The first is located at $q_z$ = 1.7 \angstrom$^-1$,
	corresponding to a real spacing of 3.7 \angstrom~. The reflection is 
	attributed to $\pi$-$\pi$ stacking between aromatic rings in the direction
	perpendicular to the membrane plane, or z-axis. For simplicity, this 
	reflection will be referred to as R-$\pi$.
        %MRS: why R in R-pi? for reflection?
	%BJC: yes, R = reflection
	\item A weak intensity line is located at exactly half the $q_z$ value of
	R-$\pi$ ($q_z$ = 0.85 \angstrom$^-1$), corresponding to a 
	real space periodic spacing of 7.4 \angstrom~. This reflection has been 
	interpreted  as 2\textsubscript{1} helical ordering of aromatic rings 
	along the z axis meaning if the positions of the aromatic rings can
	be traced by a helix, then for each turn in the helix, there should be
	two aromatic rings. For this reason it will be referred to as R-helix.
	\item A third major reflection is marked by a low intensity ring located
	at r = 1.4 \angstrom$^-1$. The real space separation 
	corresponds to 4.5 \angstrom~ which is characteristic of the average 
	spacing between packed alkane chains. This reflection will be called R-alkanes.
	\item Within R-alkanes, are four spots of higher intensity which 
	will be called R-spots. All are located $\approx 40$ degrees from the $q_z$ axis
	in their respective quadrants. In many liquid crystal systems this can be
	explained by the tilt angle of the alkane chains with respect to the xy plane. % BJC: Reference
	\item The final major reflections correspond to the spacing and symmetry of 
	the d\textsubscript{100} plane which can be related to the distance between
	pores. The feature, which will be called R-pores, is characterized by dots 
	along $q_z$ = 0. The spacing between dots is indicative of the hexagonal 
	symmetry of the packed pores. It is easiest to interpret the data by 
	radially integrating the 2D data to get a 1D curve which is shown in Figure~\ref{fig:SAXS}.
  \end{itemize}

@@

  The initial distance between layers can influence the approach towards
  equilibrium. 
  \begin{itemize}
  	\item Our choice of distance between layers results in long-term stability of 
	different configurations indicating that we have found more than one metastable
	free energy basin.
  	\item Equilibrated systems built according to the 3.7 \angstrom~ 
	layer spacing implied by R-$\pi$ are characterized by a defined, cylindrical and
	open pore structure.
	\item Aromatic rings are arranged in a helical conformation.%BJC: could potentially support with a figure. Mentioning the helical arrangmentment might makes things confusing though
        %MRS: 'basin' is not that common a term, and also only makes sense if one explicitly states what 
        %MRS: the basin is with respect to. 
	%BJC: added sentence to beginning of paragraph
        \item We will refer to this large set of configurations, with an open helical pore, as Basin A (Figure~\ref{fig:abasin}).
        %\item We will refer to this system as
        %MRS: maybe Basin O and Basin C for open and closed?
	%BJC: That works but 'capital oh' might get confused with zero
	\item Simulations of systems built with layers stacked greater than 4 
	\angstrom~ apart results in a pore structure characterized by high radial 
	disorder, while still maintaining partitioning between hydrophobic and 
	hydrophilic regions.
        %MRS: see above for clarifying ``basins''.
	\item This will be called Basin B (Figure~\ref{fig:bbasin}).
        %MRS: I don't think enough information has been presented to the reader yet for this to be 'apparent'.
	\item This LLC membrane may exist in at least two metastable states.
	\item The distinct difference in pore structure exhibited by each phase will 
	likely lead to different transport mechanisms.
	\item Because the pore structure will vary between each Basin, understanding 
	which phase exists experimentally is necessary in order to ensure we are 
	studying the system which actually dominates.  %MRS: remind people why.
  \end{itemize}
